### 2020-03-31 writeup/setup.tex
edit

Multi-task learning that is applied on heterogenous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional linear regression setting.
\begin{enumerate}
	\item {\bf Negative transfer:} we establish a fundamental limit that is caused by model shift.
	Moreover, this cannot be corrected via changing the model capacity or reweighting the tasks.
	\item {\bf De-noising effect of MTL:} we show that multi-task transfer has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
\end{enumerate}

@@

@@

In addition to covariate shift, in general the single-task models can also be different across different tasks.
\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.}
%We remove the assumption that the models are the same.
%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
%\begin{align}
%	Y_i = X_i \beta_i + \varepsilon_i.
%\end{align}

@@

\todo{setup motivation and notations}
We would like to get insight on how covariate and model shifts affect the rate of transfer.
For the case of two tasks, we can get precise rates using random matrix theory.
For the sake of clarity, we call task 1 the source task and task 2 the target task,
i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.

>>>>

Multi-task learning that is applied on heterogenous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional linear regression setting.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task transfer has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
	\item {\bf Negative transfer from model shift:} we establish a fundamental limit that is caused by model shift.
	Moreover, this cannot be corrected via changing the model capacity or reweighting the tasks.
\end{enumerate}

@@

In general the single-task models can also be different across different tasks.
We shall argue that in addition to the bias and variance terms of generalization error, model shift introduces a third term which is the bias caused by model shift.

\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models?}
%We remove the assumption that the models are the same.
%The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
%\begin{align}
%	Y_i = X_i \beta_i + \varepsilon_i.
%\end{align}

@@

@@

%\todo{setup motivation and notations}
We would like to get insight on how covariate and model shifts affect the rate of transfer.
We will consider the high-dimensional setting where for the target task, its number of data points is a small constant times $p$.
This setting captures a wide range of applications of multi-task learning where we would like to use auxillary task data to help train tasks with limited labeled data.

\paragraph{The case of two tasks.}
We can get precise rates using random matrix theory.
For the sake of clarity, we call task 1 the source task and task 2 the target task,
i.e. $\beta_1 = \beta_s$ and $\beta_2 = \beta_t$.
We introduce the following notations for the high-dimensional setting
\[ c_{n_1} \define \frac{n_1}{p} \to c_1, \quad c_{n_2} \define \frac{n_2}p \to c_2, \quad \text{as } \ n_1, n_2\to \infty, \]
for some constants $c_1, c_2 \in (1,\infty)$.

% \gamma_n:= \frac{p} {n_1 + n_2} \to \gamma,
